DTOADQ

### 2017-11-27 testdocs/test.tex
doicumentation

  In order to compute a normal of an SDF, you must perform a gradient approximation: the central distance onf the SDF at
  P. For example, the difference quotient:
  \[\frac{(f(x+h) - f(x))}{h}\]

  \section{OpenCL}
	OpenCL, and GPU programming in general, is where I am least knowledgeable or interested. Well, OpenCL is easy to work with, and I wrote my own OpenCL module to handle OCL in a rather convenient method, for example, the DTOADQ kernel call looks as such:
	\begin{lstlisting}
	shared_info.image.Lock(); // Acquire OCL Mem from OGL image object
	ocl.Run(
	  ocl.CLStoreMem(shared_info.rw_image),
	  shared_info.image.RWrite(),
	  ocl.CLStoreMem(shared_info.image_metadata),
	  shared_info.camera,
	  shared_info.timer,
	  ocl.CLPredefinedMem(imgs),
	  ocl.CLStoreMem(shared_info.ocl_material),
	  debug_values,
	  ocl.CLStoreMem(shared_info.rng_states),
	  // kernel size
	  shared_info.image.x, shared_info.image.y
	);
	shared_info.image.Unlock();

@@

    Calculating probability distribution functions is a very vital component in
    Monte Carlo Sampling. The PDF states the probability of a random variable to
    take the form of a given input. Its usefulness comes when contributions from
    many Monte Carlo samples have a different weight. That is, one sample may
    have a higher probability distribution, and thus a higher contribution to
    the path. That's the strategy behind Monte Carlo;
    \begin{align}
      \int f(x) \approx \frac{1}{N}\Sigma_0^N\frac{f(x)}{p(x)}
    \end{align}
    The PDF applies to everything from path contributions, solid angles of a
    BRDF, uniformly sampling a sphere, etc. I had a difficult time understanding
    these, and more importantly, how to calculate them for a given formula. The
    biggest conceptual barrier is that, for example, given a solid angle in a
    hemisphere $\Omega$, the probability for a random uniform $X$ to equal
    $\omega$ is 0. That's not what the PDF calculates, instead, it's the
    probability that a random uniform $X$ could potentially equal $\omega$ when compared to other $\omega\:$s. In other words, it's about comparing the probability of $X$ to equal $\omega$ when compared to another theoretical z$\omega$.

    The good thing is that calculating these are relatively easy. There's a
    reliable three-step process. The first is to
    find the cumulative distribution function $CDF = Pr(X \leq x)$. Where $Pr$
    is the probability, $X$ is a uniformly random variable, and $x$ is a known
    constant. In other words, this gives the probability that, for a formula
    $P$, where $X \in \Omega$, and $\Omega$ is the set of all possible values
    for $CDF$,
    that $X \leq x$. The second step is to take the derivative of this, so for
    PDF $p$
    \begin{align}
      p(x) = \frac{dCDF(x)}{dx}
    \end{align}
    And the final step is to verify that the PDF is correct by integrating it
    over $\Omega$, this final value should equal 1. This makes sense intuitively
    -- it is a probability after all, so the sum of the probabilities of every
    possible input must be 1.
    For an example, how I calculated the PDF of an area light source
      $L^0_e(v) = L_o(P, \omega_o)$ 
    is quite simple. Firstly,the area light is defined as a sphere, and thus our
    set of all possible values is correlated to surface area:
    $\Omega = [0,\:2.0f*\tau*R^2]$. Thus,
    \begin{align}
      CDF(x) = Pr(X \leq x) = \frac{x}{2.0*\tau*R^2}\\
      p(x) = \frac{dCDF(x)}{dx} = \frac{1.0}{2.0*\tau*R^2}\\
      \int_0^{\Omega}p(x)dx = 1.0
    \end{align}
    In code
    \begin{lstlisting}
      float Light_PDF ( Emitter* m ) {
        return 1.0f/(2.0f*TAU*SQR(m->radius));
      }
    \end{lstlisting}
    The more interesting aspect, in this example, is actually generating the
    uniformly distributed samples of a sphere. The naive method gives incorrect
    distributions.TODO {page 774}

    The most obvious way to calculate this is the six-point gradient; where for
    each axis you compute $f(x+h) - f(x-h)$, and normalize the result. This
    returns a vector pointing in the direction where the map's SDF changes the
    most: the normal. A four point gradient is possible; as long as each each
    point of the gradient is multiplied by $\epsilon$ before normalizing. The
    speedup from six to four is worthwhile, as computing each gradient is
    expensive as it involves a sdf map call. There are more utilities with
    gradients not yet currently provided in DTOADQ but are worth mentioning, a
    few are: an additional normal call using an alternative (higher-quality) SDF
    map can be used to compute a 'normal' bumpmap, and analyzing the gradient by
    hand allows a cheap normal computation of primitives such as a spheres.

    Rendering equation with solid angle:
  \begin{align}
    L_o(P, \omega_o) = L_o(P, \omega_o) + \int_{\Omega}f_s(P, \omega_i,
    \omega_o) L_i(P, \omega_i) cos\Theta_i d\omega_i
  \end{align}
    To get from solid angle to path, consider:
  \begin{align}
    f_s(v \rightarrow \dot{v} \rightarrow \ddot{v}) &= f_s(P, \omega_i,
                                                      \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e(P, \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e^0(v) L_e^1(v \rightarrow \dot{v})
  \end{align}
    That is, instead of looking at a point $P$ with an incoming and outgoing
    angle $(\omega_i,\:\omega_o)$, look at the path from $P_{-1}$ ($v$) to
    $P_{+1}$ ($\ddot{v}$). More accurately, it's the transport between
    three different surfaces of the scene. In terms of SDFs, the surface
    is every point on an SDF map where $|map| \leq \epsilon$. There's no longer
    any integration over a hemisphere with solid angle $\omega_i$, it's now over
    every single surface in the scene. This will be explained in detail later.
\\
    In the case of $L_e$,
    DTOADQ [at least, for now], only has support for area-light. Thus consider:

>>>>

  In order to compute a normal of an SDF, you must perform a gradient approximation: the central distance onf the SDF at
  P. For example, the difference quotient:
  \[\frac{(f(x+h) - f(x))}{h}\]
  The most obvious way to calculate this is the six-point gradient; where for
each axis you compute $f(x+h) - f(x-h)$, and normalize the result. This
returns a vector pointing in the direction where the map's SDF changes the
most: the normal. A four point gradient is possible; as long as each each
point of the gradient is multiplied by $\epsilon$ before normalizing. The
speedup from six to four is worthwhile, as computing each gradient is
expensive as it involves a sdf map call. There are more utilities with
gradients not yet currently provided in DTOADQ but are worth mentioning, a
few are: an additional normal call using an alternative (higher-quality) SDF
map can be used to compute a 'normal' bumpmap, and analyzing the gradient by
hand allows a cheap normal computation of primitives such as a spheres.
  \section{OpenCL}
	OpenCL, and GPU programming in general, is where I am least knowledgeable or interested. Well, OpenCL is easy to work with, and I wrote my own OpenCL module to handle OCL in a rather convenient method, for example, the DTOADQ kernel call looks as such:
	\begin{lstlisting}
	shared_info.image.Lock(); // Acquire OCL Mem from OGL image object
	ocl.Run(
	  ocl.CLStoreMem(shared_info.rw_image),
	  shared_info.image.RWrite(),
	  ocl.CLStoreMem(shared_info.image_metadata),
	  shared_info.camera,
	  shared_info.timer,
	  ocl.CLPredefinedMem(imgs),
	  ocl.CLStoreMem(shared_info.ocl_material),
	  debug_values,
	  ocl.CLStoreMem(shared_info.rng_states),
	  // kernel size
	  shared_info.image.x, shared_info.image.y
	);
	shared_info.image.Unlock();

@@

    Calculating probability distribution functions is a very vital component in
    Monte Carlo Sampling. The PDF states the probability of a random variable to
    take the form of a given input. Its usefulness comes when a Monte Carlo sample has a smaller or higher total contribution compared to other samples. That is, one sample may
    have a higher probability distribution, and thus a higher contribution to
    the path. That's the strategy behind Monte Carlo;
    \begin{align}
      \int f(x) \approx \frac{1}{N}\Sigma_0^N\frac{f(x)}{p(x)}
    \end{align}
    The PDF applies to everything from path contributions, solid angles of a
    BRDF, uniformly sampling a sphere, etc.

    The
    biggest conceptual barrier is that, for example, given a solid angle in a hemisphere $\Omega$, the probability for a random uniform $X$ to equal $\omega$ is 0. That's not what the PDF calculates, instead, it's the
    probability that a random uniform $X$ could potentially equal $\omega$ when compared to other $\omega\:$s.

    The good thing is that calculating these are relatively easy. The first step is to
    find the cumulative distribution function $CDF = Pr(X \leq x)$. Where $Pr$
    is the probability, $X$ is a uniformly random variable, and $x$ is a known
    constant. This gives the probability that, for a formula
    $P$, where $X \in \Omega$, and $\Omega$ is the set of all possible values
    for $CDF$,
    that $X \leq x$. Then the PDF $p$ is defined by the derivative of CDF. To verify that the PDF is correct, integrate it
    over $\Omega$, this final value should equal 1. This makes sense intuitively
    -- it is a probability after all, so the sum of the probabilities of every
    possible input must be 1.
    For an example, how I calculated the PDF of an area light source
      $L^0_e(v) = L_o(P,\:\omega_o)$ 
    is quite simple. Firstly,the area light is defined as a sphere, and thus our
    set of all possible values is correlated to surface area:
    $\Omega = [0,\:2.0f*\tau*R^2]$. Thus,
    \begin{align}
      CDF(x) = Pr(X \leq x) = \frac{x}{2.0*\tau*R^2}\\
      p(x) = \frac{dCDF(x)}{dx} = \frac{1.0}{2.0*\tau*R^2}\\
      \int_0^{\Omega}p(x)dx = 1.0
    \end{align}
    In code
    \begin{lstlisting}
      float Light_PDF ( Emitter* m ) {
        return 1.0f/(2.0f*TAU*SQR(m->radius));
      }
    \end{lstlisting}

  The rendering equation is:
  \begin{align}
    L_o(P, \omega_o) = L_e(P, \omega_o) + \int_{S}f_s(P, \omega_i,
    \omega_o) L_i(P, \omega_i) \vert cos\theta_i\vert d\omega_i
  \end{align}

  Where:
  	 $Lo(P,\:\omega_o)$ is the radiance at point $P$ in space towards direction $\omega_o$.

  	 $L_e(P,\:\omega_o)$ is the emittance at point $P$ towards $\omega_o$ (such as a lamp).

  	 $S$ is the unit sphere in which the angle $\omega_i$ is integrated over in respects to the normal at $P$. Also, this means, implicitly, that the equation is in respects to solid angle; the angle at which a primitive $A$ subtends $B$.

  	 $f_s$ is the Bidirectional Scattering Distribution Function. This will be detailed in the BSDF chapter, suffice it to say, it describes how photons are scattered (or absorbed) from point P in space from direction $\omega_i$ towards $\omega_o$ -- either through reflection (BRDF), or transmittance (BTDF). In volumetric path tracing, there is also subsurface scattering.

  	 $L_i(P, \omega_i)$ is the rendering equation at P from $\omega_i$

  	 And $cos\theta_i$ is the normal attenuation.

  Conceptually, this is the behavior of photons bouncing off several surfaces of a scene. While it's a very simple model, it's impossible to solve analytically for anything but the most simple of scenes, mostly due to, for example, the radiance at $P0$ relies on $P1$, and $P1$ relies on $P0$.

  Another thing to remember is that while it is shown to be integrated over a sphere, it is almost always, and will be for the rest of this document, integrated over hemisphere $\Omega$ using either $f_r$ or $f_s$.

  Unfortunately, this formula does not work very well in regards to bidirectional path tracing. The reason is because BDPT requires to work in terms of surfaces rather than solid angle, ei, $v_0 \rightarrow v_1$. So now the rendering equation must be transformed from solid angle to surfaces:
  \begin{align}
    f_s(v \rightarrow \dot{v} \rightarrow \ddot{v}) &= f_s(P, \omega_i,
                                                      \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e(P, \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e^0(v) L_e^1(v \rightarrow \dot{v})
  \end{align}
    That is, instead of looking at a point $P$ with an incoming and outgoing
    angle $(\omega_i,\:\omega_o)$, look at the path from $P_{-1}$ ($v$) to
    $P_{+1}$ ($\ddot{v}$). More accurately, it's the transport between
    three different surfaces of the scene. In terms of SDFs, the surface
    is every point on an SDF map where $|map| \leq \epsilon$. There's no longer
    any integration over a hemisphere with solid angle $\omega_i$, it's now over
    every single surface in the scene. This will be explained in detail later.
\\
    In the case of $L_e$,
    DTOADQ [at least, for now], only has support for area-light. Thus consider:
